\chapter{Dynamic Programming}\label{chp:dynamic_programming}

% \lipsum[100]
% \blindtext[10]



The word \textbf{Dynamic} in Dynamic Programming refers that our computation complexity for the given problem can be reduced if:

\begin{enumerate}[(i)]
    \item Current state of the problem depends upon previous state solved.
    \item previous state has been already precomputed \& we have also saved their state.
\end{enumerate}


As we know recursion is way, in which current problem can be expressed in term of smaller sub-problem. Hence, writing the current state of problem in recursive way is the main step in solving question by dynamic programming.

\vspace{5mm}
% \addvspace{10cm}
Steps to Solve Dynamic Programming Question:
\begin{enumerate}[(i)]
    \itemsep0em 
    \item Express the current state of problem in recurrance relation.
    \item solve the problem in recursive way. (by considering all the edge case).
    \item Compute time complexity of recursive solution. Then compute time complexity of memoized solution.
    \item If memoized time complexiy is okay $\Rightarrow$ this is the solution.
    \item If memoized time compleixy is not okay $\Rightarrow$ express solution in alternative recurrance (same as modifying the recursive function defination) way; such that less variable term are mentioned in the recurrance relation.
\end{enumerate}

\section*{Dynamic Programming Questions}
\paragraph{type1} We will list \& discuss some of the common question pattern from this paradigm.

\input{subset-sub.tex}
\input{coin-change.tex}
\input{rod-cutting.tex}
\input{matrix-multiplication.tex}
\input{lcs.tex}
\input{lis.tex}
\input{lisa.tex}

\vspace{3cm}

Pratice Questions:
(LC 1547) Minimum cost to cut a stick.

Exercise Question:
(a) For LC1547 print the optimal ordering.

Pratice Hints:


Exercise Solution:
LC

Please Categorize:
\begin{enumerate}[(i)]
    \item 
     LC 2218 : $f(idx,\_)$ = maximum total value of coing we can pick if we are allowed to pick coins from from arr[0...idx]\\
     now at idx, we have the option to chose either \begin{verbatim} {1}, {1,2}, {1,2,3}... {1,2,...min(k,size)} \end{verbatim} options
        
     we will take the best from all the option.
    
     \item LC 1105: with $f(idx,\_)$ defination as same as 2218.\\
     At idx, we can chose either 1 or 2 or 3 books, ... n books. We will take the best of all.

     \item LC 1547 (simple variation of rod-cutting)
     \item (LC 1092- Shortest Common Supersequence)
     \item LC801 Minimum Swaps To Make Sequences Increasing 
\end{enumerate}

\vspace{5cm}
Comment About Excercise Problem (And possibly have hint too)
\begin{enumerate}[(i)]
    \item LC801: Nice problem where state information can be transferred to other variable + if we use base case to detect invalid case, then code can be greatly simplified.
\end{enumerate}
