\begin{problem}{Edit Distance}
    You are given two string s1 and s2. Your task is to convert s1 to s2. But you have permitted following operations: Insert,Delete and Replace.

    \footnotetext{LC72}
\end{problem}

\begin{solution}[ways at idx]
    First try to formulate the question in term of recursive ways.

    We need to convert s1 to s2, but we have allowed only 3 operations.
    Hence, \intution{think of ways to fill the ansString, when we are at index idx.}

    \begin{code}
        int findAns(int i,int j,const string &s1,const string &s2)
        {
            cc printf("[%d,%d]\n",i,j);
            if(i==s1.size() && j==s2.size()) return 0;
            if(i>=s1.size()) return s2.size()-j; //add this much entry to s1
            if(j>=s2.size()) return s1.size()-i;  //delete this much entry from s1
            
            int &mans = mem[i][j];
            if(mans != -1) return mans;
            
            //now try to create new ansString.
            //to populate idx of answer string, you can have three operations
            
            int val1 = 1 + findAns(i,j+1,s1,s2); //insertion 
            int val2 = 1+ findAns(i+1,j,s1,s2); //deletion
            int val3 = 1 + findAns(i+1,j+1,s1,s2); //replacement
            int val4 = INT_MAX; //do nothing
            
            if(s1[i] == s2[j])
                val4 = findAns(i+1,j+1,s1,s2);
            
            return mans= min({val1,val2,val3,val4});
        }
    \end{code}
    
\end{solution}

\begin{pratice}
    \begin{asparaenum}
        \item Follow-Up: Can you devise the solution if the iCost,rCost and dCost values are not same?
    \end{asparaenum}
\end{pratice}