\chapter{LogicMojo Question List}\label{chp:LogicMojo}

This chapter list down all the question I have solved from logicmojo.
Revising it once again will make sure, you at least have enough grasp of one of the learning path!

I think it will make your understand and revision up to | 70% |

\hl{You need to mark each question complete, if you written the pragamatic code for each}

\rfl{Irrespective of the desired complexity asked, always try to start from brute force and then list all ways the given problem can be solved.}

Its okay, if this section repeates problem from section.

{\smaller[1] 
\begin{exercise}[Must Solve Stack List]

    \ctext{ Standard Sorting Things}

    \begin{compactenum}
        \item Can you list down at least 5 type of sorting alorithm?
        \item Please implement following sorting algo with pragamatic code:
        \begin{compactenum}
             \item Merge Sort 
             \item Quick Sort
             \item  Heap Sort
             \item Counting Sort

             \item Bubble Sort
             \item Insertion Sort
             \item Selection Sort
             
             \item Radix Sort
             \item Bucket Sort
             \item  TODO mark as done, when you have added pragmatic code for each
             
        \end{compactenum}

        \item Problems utilizing sorting technique:
            \begin{compactenum}
                \item Find $ k^{\text{th}} $ largest element in an unsorted array using quicksort. (LC215)
                \item Dutch National Flag Problem (\href{https://leetcode.com/problems/sort-colors/description/}{LC75})
                \item Inversion count using merge sort
                \item Inversion count using quick sort
            \end{compactenum}
        
        \item What is stable sort algorithm? can you list down few?
        \item You need to utilize paraller processing while sorting? which algo would you chose and why?
        \item You have a large dataset to sort, which sorting algo would you use?

        \newlist{Sorting Alorithm Based Problems}
        \item Find maximum element in rotate sorted array.
        \item Find given element k, in a rotate sorted array.
        \item lowerbound and upperbound for normal array without duplication
        \item above with duplicates
        \item above with duplicate + sorted sorted array
    \end{compactenum}

    % 2nd set
    \ctext{cont.. logicmojo list}
    \begin{compactenum}
    \item move all zero to the end of the array while maintaing the relative order or non-zero element.
    \item Jump Game Problem, but this time solve using array traversal. 
    \href{https://leetcode.com/problems/jump-game/description/}{LC55}
    \footnote{There exist DP solution, but this time you just iterate and try to solve}
    \item remove duplicate element from sorted array in place.
    
    \item Write an algorithm to find out next greater number to given number with the same set of digits
    \item Find an element in array (=k), before which all number are less than k, and after which all greater than k.
    \item Find if two rectange overlap or not.
    \item List of arrival and departure time is given, Find the minimum number of platforms are required for the railway as no train waits.
    \\Similar Problems
    \begin{compactenum}
        \item LC56 Merge Interval,
        \item LC3169 Count Days without meeting (sorted by start time or end time)
        \item LC453
        \item LC252,LC253 Meeting Rooms
        \item LC1235 Maximum Profit in Job Scheduling
        \item LC3414 Maximum Score of non-overlapping interval.
        \item Try to solve by soring start time, then end time $<-$notice the logic difference
    \end{compactenum}
    \vspace{4pt}
    \item Distribute candy to children  with some rule. LC135
    
    \item print matrix in spiral order in $O(1)$ space complexity.
    \item print matix element in diagonal order in $O(1)$ space complexity.
    \item Array of size n, having integer in 1 to n with some duplicates. you need find frequency of all element in array in $O(n)$ time and $O(1)$ space.
    \item find majority element of the array in best time complexity. LC169,LC229
    
    \item Stock Selling Problem
    \begin{compactenum}
        \item you can hold a single stock a time. LC122
        \item you are allowed at most 2 transaction LC123
        \item at most k transactions. LC188
        \item with cooldown days LC309
        \item with transaction fee LC714
    \end{compactenum}

\item remove duplicate letter from string in $O(1)$ time complexity.
\item Rotate the matrix clockwise direction by $90 ^\circ $ in $O(1)$ space complexity.
\item  You are in a party of N people, where only one person is known to everyone. Such a person may be present at the party, if yes, he/she doesn’t know anyone at the party. Your task is to find the celebrity at the party.
\item Find subarray whose sum is ZERO. the array has both positive and negative number.
\begin{compactenum}
    \item 2sum problem
    \item 3sum problem
\end{compactenum}
\item Find next smallest palindrome larger than this given number x.
\item Find the contiguous subarray within an $array[]$ of length N which has the largest sum in Time Complexity $O(n)$ and Space Complexity $O(1)$. (aka Kadan's Algorithm)
\begin{compactenum}
    \item Can you extend/modify above algo to find subarray that has sum exactly k?
\end{compactenum}
\item Find kth smallest element in that in an unsorted integer array in Time Complexity O(n) and Space Complexity $O(1)$. (Hint: use quicksort) 
\item Given an array of integers and a number K. Find the count of distinct elements in every window of size K in the array. \constrain{ $TC (n)$, $SC (n)$ }
    
\vspace{5pt}

\item Given an array where every element occurs two times, except one element which occurs only once. Find the element that occurs once in $O(1)$ space. (Hint: use xor)

\item Given an array in which all numbers except two are repeated once. (i.e. we have 2n+2 numbers and n numbers are occurring twice and the remaining two have occurred once). Find those two numbers in the most efficient way.
\item Find square root of Guven Num without sqrt() function in Time Complexity $O(Logn)$ and No Space Complexity. (Hint: can you find the binary search solution too?)
\item A 2-D array of 1's and 0's is given. Find the row with max 1's in Time Complexity $O(nlogn)$ and Space Complexity $O(1)$ . The array is sorted row wise.

\vspace{5pt}
\item Trapping rainwater problem. LC42
\begin{compactenum}
    \item 2D version LC407, too hard
    \item LC11 Container with most water.
\end{compactenum}

\vspace{3pt}
\item Given an array $A[]$ of N positive integers. The task is to find the maximum of $j - i$ with the constraint of $A[i] <= A[j]$. Time Complexity : $O(n)$Space Complexity : $O(n)$.

\item Given an unsorted Array, Find the count of Inversion required to make this array sorted in Time Complexity:$O(nlogn)$

\item There are two sorted arrays A and B of size m and n respectively. Find the median of the two sorted arrays. The overall run time complexity should be $O(log n)$ and Space Complexity $O(1)$. (Hint: can you solve again usign binary search this time?)

\item Given two sorted arrays of size m and n respectively, you are tasked with finding the element that would be at the k’th position of the final sorted array Time Complexity: $O(log n + log m)$.

\item Design a data structure which performs the following operations(Insert an element/Remove an element /find random element) in $O(1)$ time.
\item You need to design a data structure which support below operation in O(1) time complexity
    \\ Insert() add element
    \\ remove() delete element 
    \\ findMiddle()   return middle element
    \\ deleteMiddle() delete the middle element.

\item Given two strings string1 and string2 , return the minimum window in string1 which will contain all the characters in string2 in Time Complexity $O(n)$ and Space Complexity $O(1)$.
\item You are given a string. You have to find the smallest substring which contains all the distinct characters of the given string.
Try solving this question in O(n), using the sliding window technique.

\end{compactenum}

% \newlist{Binary Tree Problems1}
\newpage
\ctext{Binary Tree}
\begin{compactenum}
    \item Tree traversal, write code for pre-order, in-order, post-order traversal code.
    \item Given a binary search tree, write a function to find the kth Largest element in it.
    \item Convert BT to DLL such that the left pointer of the node should be pointing to the previous node in the doubly linked list, and the right pointer should be pointing to the next node in the doubly linked list in Time Complexity $O(n)$ and Space $O(Height)$
    \item Check if a given binary tree is height-balanced or not. ( a height-balanced binary tree is a binary tree in which the left and right subtrees of every node differ in height by no more than 1.)
    \item Print all the nodes which are at k distance from the root. Root of the Binary tree and K is given as Input in Time Complexity $O(n)$.
    \item Given a root node reference of a BST and a key, delete the node with the given key in the BST. Return the root node reference (possibly updated) of the BST.
    Basically, the deletion can be divided into two stages:Search for a node to remove.If the node is found, delete the node.
    \item print all the nodes k distance from any random node in the tree in Time Complexity O(n) and Space Complexity O(n) 
    \item Given a Binary Tree and a positive integer k, print all nodes that are distance k from a leaf node k distance from a leaf means k levels higher than a leaf node. For example, if k is more than the height of the Binary Tree, then nothing should be printed. Expected time complexity is O(n) where n is the number nodes in the given Binary Tree.
    \item Given a binary tree, determine if it is a valid binary search tree (BST).
    Assume a BST is defined as follows:
    The left subtree of a node contains only nodes with keys less than the node's key.
    The right subtree of a node contains only nodes with keys greater than the node's key.
    Both the left and right subtrees must also be binary search trees.
    \item Given a binary tree, print the values of nodes which would be present in bottom of view of binary tree.
    \item  Given a binary tree, find the lowest common ancestor (LCA) of two given nodes in the tree. Let T be a rooted tree. The lowest common ancestor between two nodes n1 and n2 is defined as the lowest node in T that has both n1 and n2 as descendants.
    \item We have the inorder and postorder traversal sequence of a binary tree to generate the Binary tree.
    \item Find the distance between two keys in a binary tree, no parent pointers are given. Distance between two nodes is the minimum number of edges to be traversed to reach one node from other.
    \item The diameter of a binary tree is the length of the longest path between any two nodes in a tree. Find diameter of tree in Time Complexity O(n).
    \item Given a binary tree, find the largest subtree which is a Binary Search Tree (BST), where the largest means subtree with the largest number of nodes in it.
    \item Printing the left view of a binary tree involves printing the left-most node, at each level.
    \item Two nodes of a binary tree are cousins if they have the same depth, but have different parents. We are given the root of a binary tree with unique values, and the values x and y of two different nodes in the tree.Return true if and only if the nodes corresponding to the values x and y are cousins.
    \item Algorithm to print Binary Tree nodes level by level in reverse order. It means all the nodes at the last level should be printed first followed by the nodes of second last level and so on in Time Complexity O(n) and Space Complexity O(n).
    \item Given a binary tree, return the Iterative  preorder traversal of its nodes' values
    \item Binary tree is given and you need find vertical sum of the nodes that are in same vertical line in Time and Space Complexity O(n).
    \item Find the maximum sum leaf to root path in a Binary Tree. Means in all the paths from root to leaves, find the path which has the maximum sum.
    \item Given a binary tree, print its nodes level by level in spiral order in Time and Space Complexity O(n).
    \item Given a binary tree, return the Iterative inorder traversal of its nodes' values.
    \item Design an algorithm and write code to serialize and deserialize a binary tree. Writing the tree to a file is called 'serialization' and reading back from the file to reconstruct the exact same binary tree is 'deserialization' in Time and Space Complexity O(n).
    \item Algorithm to Connect all the nodes in same level of a binary tree in Constant Space and O(n) Time Compelxity.
    \item Given a Binary tree and a key in the binary tree, find the node right to the given key. If there is no node on right side, then return NULL. Expected time complexity is O(n) where n is the number of nodes in the given binary tree.
    \item Two n-ary trees given , Check if they are mirror of each other or not In Time and Space Complexity O(n).
    \item Mirror of a Tree: Mirror of a Binary Tree T is another Binary Tree M(T) with left and right children of all non-leaf nodes interchanged.
    \item Given a non-empty binary tree, find the maximum path sum in Time Complexity O(n).
    \item Given a Binary Tree, Convert this to a tree where each node contains the sum of the left and right sub trees in the original tree. The values of leaf nodes are changed to 0.
    \item 
    


\end{compactenum}

\newpage
\ctext{Linked List}
\begin{compactenum}
    \item Linked list, sentinal node in linked list.
    \item Given a linked list print the list (a) iterative (b) recursive
    \item Given two sorted linked lists, merge them so that the resulting linked list is also sorted in Time Complexity O(n) and Space Complexity(1).
    \item Check Single Linked List is Palindrome or not. (good use of recursion stack!)
    \item You are given a linked list as input , you need to sort it using merge sort algorithm using merge sort in Time Complexity O(nLogn).
    \item Given two numbers represented by two linked lists, write a function that returns the sum list. The sum list is linked list representation of the addition of two input numbers. It is not allowed to modify the lists. Also, not allowed to use explicit extra space.
    \item You are given a double Link List with one reference of each node pointing to the next node just like in a single link list. The second reference however can point to any node in the list and not just the previous node.Write a program in O(n) time which will create a copy of this list.
    \item Given a Linked List and a number n, write a function that returns the value at the n'th node from the end of the Linked List.
    \item Given a linked list, reverse the nodes of a linked list k at a time and return its modified list in Time Complexity O(n).
    \item Write a program to find the node at which the intersection of two singly linked lists begins.
    \item Linked list is given also, in addition to the next reference, each node has a child pointer that can point to a separate list. With the head node, flatten the list to a single-level linked list in Time Complexity O(n).
    \item Given a Linked List of integers, write a function to modify the linked list such that all even numbers appear before all the odd numbers in the modified linked list. Also, keep the order of even and odd numbers same.
    \item Rearrange a Single Linked List in Time Complexity O(n) and Space Complexity O(1) such one node selected from start next node from end.
    \item some important lc problems (todo)
\end{compactenum}

\newpage
\ctext{Hashing / HeapSort}
\begin{compactenum}
    \item Min/Max Heap Implementation, heapify operation implementation. (alread covered in sorting section)
    \item Given an array of strings, return all groups of strings that are anagrams.
    \item Given a stream of characters, find the first non-repeating character from stream. You need to tell the first non-repeating character in O(1) time at any moment.
    \item Design and implement a data structure for Least Recently Used (LRU) cache. It should support the following operations: get(key)and set(key,value).
    \item Given an array  of n integers and an integer target, Find if there elements a, b, c, and d in integers present in array  such that a + b + c + d = target. Find unique quadruplets in the array which gives the sum of target .
    \item Write an efficient algorithm to convert a given number into words. 
    \item Given that integers are being read from a data stream. Find median of all the elements read so far starting from the first integer till the last integer. The data stream can be any source of data, example: a file, an array of integers etc..
    \item Given k sorted array, write an efficient algorithm to merge them into one sorted array .
    \item Given two strings string1 and string2, the task is to find the smallest substring in string1 containing all characters of string2.
    \item Given two integer array, Sort first array based on the Order of second array in Time and Space Complexity O(n).
\end{compactenum}

\ctext{Backtracking}
\begin{compactenum}
    \item you should do recurion before it! (recursion is the root of problem solving paradigm)
    \item How recursion works. lecture , how to debug its case and how to understand it.
    \item find an arrangement of N queens on a chess board, such that no queen can attack any other queens on the board. The chess queens can attack in any direction as horizontal, vertical, horizontal and diagonal way.
    \item Given n pairs of parentheses, write a function to generate all combinations of well-formed parentheses.
    \item You are given a string and you are supposed to print all the distinct permutations of the string.
    \item Given a set of array numbers (without duplicates) and a target number (target), find all unique combinations in the array where the numbers sum to target.The same repeated number may be chosen from array unlimited number of times.
    Note: All numbers (including target) will be positive integers. The solution set must not contain duplicate combinations
    \item Given a maze, NxN matrix.matrix[0][0] (left top corner)is the source and matrix[N-1][N-1](right bottom corner) is destination. There are few cells which are blocked, means rat cannot enter into those cells. Rat can move in direction ( forward,down). A rat has to find a path from source to destination.
    \item Given a set of positive integers, find all its subsets.
    \item Given a square chessboard of N x N size, the position of Knight and position of a target is given. We need to find out minimum steps a Knight will take to reach the target position.
    \item Given an integer x and a positive number n, write a efficient algorithm to computes $x^n$.
    \item Given a sudoko puzzle, solve this sudoko puzzle by using backtracking algorithm .
    \item Given a string containing digits from 29 inclusive, return all possible letter combinations that the number could represent. A mapping of digit to letters (just like on the telephone buttons) is given below. Note that 1 does not map to any letters.
    \item checkout lc problems for more backtracking/recursion problems(todo list)
\end{compactenum}

\ctext{Stack/Queue}
\begin{compactenum}
    \item Implement Stack using array as base data structure. Can you try to use circular array?
    \item Implement queue using array as base data structure.
    \item Circular queue implementation.
    \item Given n non-negative integers representing the histogram's bar height where the width of each bar is 1, find the area of largest rectangle in the this histogram.
    \item Given a string s containing just the characters '(', ')', '{', '}', '[' and ']', determine if the input string is valid.An input string is valid if: (a) Open brackets must be closed by the same type of brackets. (b) Open brackets must be closed in the correct order.
    \item Design a data structure which support push()/pop()/findminimum() operation in O(1) time.
    \item Given an input string, reverse the string word by word.
    \item Given a binary matrix, find the maximum size rectangle binary-sub-matrix with all 1's.
    \item Given an array, print the Next Greater Element for every element. The Next greater Element for an element a is the first greater element on the right side of a in array. Elements for which no greater element exist, consider next greater element as -1.
    \item Given an array and an integer K, find the maximum for each and every contiguous subarray of size k.
    \item for monotonic queue problem check lc path (todo)
\end{compactenum}

\ctext{Grap Algorithm}
\begin{compactenum}
    \item Treat below problems just as a question bank, the theory part is covered in the alog pdf, which uses lectures of great teacher shai simonson!
    \item Graph implementation using adjencdenty list in c++, java and print it.
    \item Given a undirected graph, write an algorithm to find out whether graph contains cycle or not in Time Complexity O(Vertex + Edge) and Space Complexity O(Vertex).
    \item Given a 2d matrix, find a path from the top left corner to bottom right corner. Assume there exists at least one path, and you only need to find one valid path. You can move up, right, down, left at any position with extra Space Complexity O(m + n).
    \item The topological sort algorithm takes a directed graph and returns an array of the nodes where each node appears before all the nodes it points to.
    \item Given a 2d grid map of '1's (land) and '0's (water), count the number of islands in Time Complexity O(Vertices + Edges).
    \item Consider a matrix with rows and columns, where each cell contains either a '0' or a '1' and any cell containing a 1 is called a filled cell. Two cells are said to be connected if they are adjacent to each other horizontally, vertically, or diagonally. If one or more filled cells are also connected, they form a region. find the length of the largest region.
    \item Design and implement Dijkstra's algorithm which allows us to find the shortest path between any two vertices of a graph in Time Complexity O(Edge Log(Vertices)) A
    \item there is a Dijkastra , in which you need to execute till the queue is empty. (todo the problem here)
    \item You receive a list of non-empty words from the dictionary, where words are sorted lexicographically by the rules of this new language used by aliens. Write Algorithm to Derive the order of letters in this in Time Complexity O(edges +vertices).
    \item Given a directed, acyclic graph of N nodes.  Find all possible paths from node 0 to node N-1, and return them in any order.
    \item A matrix of m*n where each cell in the matrix have Fresh,Rotten and Empty Cell. Write algorithm to find minimum time required so that all the oranges become rotten in Time Complexity O(m*n) and Space Complexity (O*m*n) i.e extra matrix space .
    \item Given a Graph, return the BFS  traversal of its nodes.
    \item Given an m x n board of characters and a list of strings words, return all words present in the board.
    \item Write a function to find the longest common prefix string amongst an array of strings.If there is no common prefix, return an empty string "".
    \item Snake and ladder board is given as matrix, find the minimum number of dice throws required to reach the last cell from source cell in Space Complexity O(n).
    \item You are given a m x n 2D grid initialized with these three possible values.
    (a) A wall or an obstacle. 0,A gate. INF  Infinity means an empty room. Fill each empty room with the distance to its nearest gate. If it is impossible to reach a gate.
    \item A number is called as a Jumping Number if all adjacent digits in it differ by 1. The difference between '9' and '0' is not considered as 1. Given a positive number x, print all Jumping Numbers smaller than or equal to x in Time Complexity $O(Jumping_Numer)$.
    \item Write a function that returns true if a given undirected graph is tree and false otherwise. For example, the following graph is a tree.
    \item Trie is the data structure very similar to Binary Tree. Trie data structure stores the data in particular fashion, so that retrieval of data became much faster and helps in performance. Implement it in code.
    \item Design the autocomplete feature for example : Google search auto suggestion .Desired Complexity O(Length of the word) and Space Complexity O(1).
    \item Given a list of contacts that exist in a phone directory and a query string str. The task is to implement search query for the phone directory. Run a search query for each prefix p of the query string str(i.e from  index 1 to str length) that prints all the distinct recommended contacts which have the same prefix as our query (p) in lexicographical order.
    \item There are a total of n courses you have to take, labeled from 0 to n-1. Some courses may have prerequisites, for example to take course 0 you have to first take course 1, which is expressed as a pair: [0,1] Given the total number of courses and a list of prerequisite pairs, is it possible for you to finish all courses? Desired Time Complexity : O(n).
    \item some important LC problem to make it complete. (todo)
\end{compactenum}

\ctext{Dynamic Programming = Recursion with Memoization}
\begin{compactenum}
    \item identify dp, dp prolems are optimization problem. shortest/longest least/most, biggest, smallest, count. problem can be broken down into sub problem. f(idx) = f(idx-1) OR f(l,r) = f(l',r') OR f(idx,state) = f(idx',state') like these.
    
    \item DP resource is Aditya Verma \href{link}{https://www.youtube.com/watch?v=nqowUJzG-iM}, treat below question only as a question bank! 
    \item How to debug DP problem? checkout dp section in algorithm handbook's DP section.
\end{compactenum}



\end{exercise}
}