\chapter{Search Algorihtms}{\label{ch:binary_search}}

Binary Search is search algorithm that reduces the normal O(n) complexiy of search to logarithmic log(n).

To binary search we need to sort our input first. There are different sorting algorithm, a few of which are listed below.
\begin{compactenum}
    \item insertion sort
    \item bubble sort
    \item merge sort | Based on Divide and Conquere
    \item quick sort | Based on Divide and Conquere
    \item Radix sort
    \item \dots
\end{compactenum}

\begin{exercise}[Binary Search Fundamental Question List:]
    Given a sorted array write the code for following:

   \begin{compactenum}
        \item Check if element exist or not.
        \item If the element exist, return it's index else -1.
        \item If the element exist return its index,else its \verb|lower_bound|.
        \item Return \verb|lower_bound| when the array may have duplicate elements.
        \item Return \verb|upper_bound| when the array may have duplicate. How will the code change when the array do not have duplicates?
        \item use \verb|c++ stl lower_bound| to give lower bound with duplicates element.
   \end{compactenum}

   \medskip
   \begin{compactenum}      
        \item First and last occurrance of an element. (this combines all above question concept) pratice: (LC34)
        \item Find minimum element in rotate + sorted array. (LC153)
        \item (LC154) minimum in rotate+sorted when duplicate allowed.
        \item find element idx in rotate+sorted array. (LC33)
        \item find element idx in rotate+sorted array,when duplicate allowed.(LC34)
   \end{compactenum}
\end{exercise}

TO-DO: Addlower bound and upper bound image.

